The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-07-30 paper/ms.tex
dr2

\caption{\label{hrdiagram}
Hertzsprung-Russell diagram of the Smear Campaign stars (orange and teal) situated in the entire \kepler sample (black), using the Bedell \url{gaia-kepler.fun} crossmatch and calibrated distances from \citet{gaiadists}. The smear sample includes giants and hot main-sequence stars. Those giants for which TRES spectroscopy have been obtained are highlighted in teal.}
\end{figure*}

>>>>

\caption{\label{hrdiagram}
Hertzsprung-Russell diagram of the Smear Campaign stars (orange and teal) situated in the entire \kepler sample (black), using the Bedell \url{gaia-kepler.fun} crossmatch and \gaia~DR2 calibrated distances from \citet{gaiadists}. The smear sample includes giants and hot main-sequence stars. Those giants for which TRES spectroscopy have been obtained are highlighted in teal.}
\end{figure*}
